\begin{center} 
ACKNOWLEDGMENTS  
\end{center} 

First and foremost, I would like to express my sincere gratitude to my research co-advisers Dr. Hongbin Yu and Dr. Sandwip Dey.  Their patience, yet willingness to challenge me to think about my work at a deeper level have been of great inspiration.  Opening up the smart-window project and allowing me creative license to pursue its completion has been instrumental in allowing me to develop an investigative research philosophy, and a personal workflow/library for designing/running experiments, analyzing data, and reporting scientific results.  Their input on all aspects of my work (particularly their expertise in device physics and characterization), has helped me better understand, model, and describe the most salient aspects of this dissertation.  I cannot thank these two professors enough for supporting me throughout my graduate career. I would also like to thank Professor Michael Goryll, who has been a great mentor to me.  Our late-evening/weekend discussions on everything from infrared spectroscopy, microscopy, electrochemistry, all the way down the rabbit hole to state minimization using implicant tables, various legacy hardware hacks, and German cars (you know, typical nerd stuff), have always been enriching and illuminating for me.  Between all of his academic commitments (teaching, committees, senior design, research), I have no idea how he still made time to help me with my own research, and for that, I'm eternally thankful. I am also extremely grateful to Professor Terry Alford for enabling my study of organic solar cells, and all of his invaluable feedback on my research.  His support has allowed me to better understand photovoltaic characterization.

My thanks to CSSER staff, especially Jon Martin, Todd Eller, Carrie Sinclair, Timothy Eschrich, Wayne Paulson, Arthur Handuagan, and Stefan Myhajlenko for all their time and effort in equipment training. They have always been readily available upon needing assistance with any processing or characterization issues. Thanks to the LeRoy Eyring Center for Solid State Science (CSSS) staff, of whom, I would like to thank David Wright and Timothy Karcher for help with all experiments both inside and outside the facilities.  To David, thank you for guiding me for nearly a decade on the single zone growth and anneal tube furnaces, and most recently thanks to you and Dr. Emmanuel Soignard for helping me interpret high resolution X-ray diffractograms.

I would also like to acknowledge a few senior colleagues from my research group who have since graduated and carry incredible lives: Dr. Tawab Dastigir, for kicking off my practical interests in nano-materials and devices, Dr. Wei Xu, for our stimulating discussions and thorough assistance in executing experiments, Tej Belagodu, for helping me start on, guiding me throughout the entire nanowire device fabrication process, Dr. Xiaodi Sun, for our work together on the smart window project, among others.  I would like thank my peers Dr. Hanshuang Liang, Dr. Hao Wu, Seungho Ahn, Dr. Mahmoud Khdour, and Dr. Jhih-Hong Peng for their support and creating an environment conducive to quality research, and for constantly showing interest in my projects.  To the junior members I have had a chance to learn from: Jignesh Vanjaria, thanks for being my personal punching bag these last three years, but more importantly, critically collaborating on ZnMgO nanowires, and to Todd Houghton, thank you for doing most of the heavy lifting in figuring out the MicroFab printer during a period I was too busy, and for being someone I can consult on nanoparticles.  I consider the both of you colleagues for life.  To the undergraduate researchers (many of whom have gone to pursue doctorates themselves) who have facilitated my work and helped me gather data for my work: William Scheidler (NNIN REU), David Bull (FURI), Gregory Spell (FURI), Lucas Thompson (FURI), Micah Tuttle, and Thomas Fou (FURI)---thank you so much for your time take out of your busy semesters and invaluable summers.

I would like to especially recognize the few colleagues who contributed directly to this project: George Chen for electrical characterization and data visualization, Weidong Ye for electrical characterization and manuscript revising, Chelsey McAlpin for electrochromic stack fabrication and manuscript revising, Benjamin Helfrecht (REU, NNIN) for device design, fabrication and characterization trials, and model visualization, and Wai Mun (Sally) Cheung for ZnO and Ag nanowire synthesis, electrical characterization, data visualization, data analysis, and manuscript revising.  I would also like to extend my gratitude to Dr. Zhao Zhao for guiding me through the organic solar cell fabrication and characterization process, as well as providing insights on device failure.

I also take this opportunity to thank all my other research colleagues for providing useful and innovative research methods, materials, and for helping me out in general.  They include Dr. Swee Hoe Lim, Dr. Cunjiang Yu, Dr. Teng Ma, Dr. Raghuraj Hathwar, Dr. Punarvasu Joshi, Dr. Bill Lepkowski, Dr. Reza Ghajar, Maryam Shakib, Dr. Pradymna Muralidharen, Hank Detlaff, Iniyan Elongo, Sai Baluguri, Sridutt Tummalapalli, Dr. Ganesh Subramanian, Dr. Nishant Chandra,  Steve Mussi, Dr. Michael DiNezza, Dr. Derek Caselli, Dr. Shirong Zhou, Dr. Preston Webster, Dr. Maitreya Dutta, Dr. Owen Hildreth, Avinash Mamidanna, Chris Lefky, Dr. Rui Tang, Dr. Salman Manzoor, Dr. Xiaofeng Wang, Dr. Xu Wang, Dr. Shankar Ramakrishnan, Dr. Samet Arda, Arvind Shalindar, and many others not mentioned for helping me out at various times during the course of this work. 

Several sources of funding have made this work possible, and I am grateful for their support. These include the Medtronic Employee Scholarship, IEEE Phoenix Chapter Fellowship, and Center for Nanotechnology in Society Fellowship, which in total supported me for three years.  My work also received financial support by the National Science Foundation (Grant Number: 1143570) as well as NASA (Grant Number: NNX-15CG10C) through a subcontract from Structured Materials Industries, Inc., Piscataway, New Jersey.

I would also like to thank some of the important people in my life who so patiently endured the insanity throughout my tenure in the program (in no particular order): Chelsea Wegner, for being incredible through the worst of it; James Maurice Cloud, for being available since the beginning; Dion Jerel Pouncil, for including me in all your creative enterprises; Stephanie Zankman, for showing me what madness lies before a med student;  Michael Hamouda, for helping me gain perspective  while simultaneously fighting your own legal battles; Patrick Krecker, for annually giving me a glimpse into the real world; Kevin King, for helping me understand academics, pop culture, politics, and everything in between; Kelsey Marks, for our shared love of delightfully silly, cringe-inducing memes (Turquoise Jeep), and of course your unwavering support as I unraveled;  Devin Clark, for always bringing a sensible perspective to my professional endeavours; Jeffery Walloch, mutually obsessing about GM since the 90s; and Stacy Caligiuri, for your optimism and support during a major inflection point in my graduate career.  Despite graduate school compromising my ability to connect with everyone, please know I wish you the absolute best in your personal and professional lives ahead.

To members of my family, who have had an even harder time seeing me: Uncle Chung-Sheng, thank you for inspiring me to pursue a doctoral program, developing a taste for American cars, supporting my interests in photography, and for turning me into a bit of an audiophile; to my father, Mahmood, and siblings Pakeeza, Rabih, and Aleeza, whom I am hoping to see more regularly.  To my grandmother Kuei-Yueh Li, who I am looking forward to spending more time with.

Above all, this work would not have been possible without the support of my amazing mother Chia-Lan. It is impossible to completely express the gratitude I owe her. I thank her for having faith in me and encouraging me to stick it out every time I felt like giving up.  She has unconditionally supported, and dealt with the fallout of all my choices, and I could not have possibly asked for a kinder, gentler, more understanding mother.  Mom, thank you for everything.

% advisor, Professor Hongbin Yu, for his support, guidance and patience during my research. My special thanks to the dissertation committee members, Professor Ronald Roedel, , and Professor Yuji Zhao for their helpful suggestions and for serving on my dissertation committee. I am also thankful for Professor Sandwip K Dey's financial support and the use of facilities in LeRoy Eyring Center for Solid State Science. Particular thanks to my research group members: Dr. Xiao Di Sun Zhou, and Ebraheem Ali Azhar.